Data Encryption Standard Implementation 4003-482-01 RIT

### 2010-05-02 paper/paper.tex
Added examples and timing measurements

\usepackage{graphicx}
\usepackage{multicol}

\usepackage{acronym}
 \usepackage[bookmarks=false,colorlinks=false,linkcolor={black},pdfstartview={XYZ null null 1.22}]{hyperref}
\usepackage{url}

\acrodef{DES}[DES]{Data Encryption Standard}
\acrodef{TDD}[TDD]{Test Driven Development}
\acrodef{OOP}[OOP]{Object Oriented Programming}

@@

\begin{abstract}
  \ac{DES} is the 56-bit block cipher that was once used to encrypt all US Government non-classified documents.
\end{abstract}

@@

\section{Examples}
\section{Software Design}

We chose to implement DES completely in $C++$ for this project.
Both of the members our group were knowledgeable and comfortable
with $C++$ and in general the $C$ world. We felt we would have a more
generally usable and useful implementation if we went with $C++$ over
another language (Java, Python, ... ). We attempted to take advantage ac{OOP} but
were careful not to over do it and dive into downword spiral subclass's and
analysing of class cohesion. The $DES$ implementation is simply a class, with actions of encrypting and
decrypting. All state information is organized within the class. We then
implemented a $BlockMode$ class which implements a cipher block, which is
as you know, just a wrapper around $DES$. The user is then provided with
two small utility functions $encrypt$ \and $decrypt$.

@@

During the duration of the project we attempted to work in a \ac{TDD} model.
All major functions and actions have associated unit-tests which we derived from various peices of
literature on DES. These unit test's were then hooked up to run using the Google Test Framework\cite{gtest}.

\section{Original Run time Measurements}
\section{Original Run time Analysis}
\section{Revised Software design}
\section{Revised Run time Measurements}
\section{Revised Run time Analysis}
\section{Developers manual}
\section{Users Manual}

>>>>

\usepackage{graphicx}
\usepackage{multicol}
% \usepackage{acronym}
\usepackage[bookmarks=false,colorlinks=false,linkcolor={black},pdfstartview={XYZ null null 1.22}]{hyperref}
\usepackage{url}

% \usepackage{mdwlist}
% \usepackage{amssymb,amsmath}
% \usepackage{cite}
% \usepackage[T1]{fontenc}

% \acrodef{DES}[DES]{Data Encryption Standard}
% \acrodef{TDD}[TDD]{Test Driven Development}
% \acrodef{OOP}[OOP]{Object Oriented Programming}

@@

\begin{abstract}
  {DES} is the 56-bit block cipher that was once used to encrypt all US Government non-classified documents.
\end{abstract}

@@

\section{Examples}

\subsection{Example 1}
\textit{Hello}
\\\indent Original:
\begin{verbatim}
   48 65 6C 6C 6F 0A
\end{verbatim}
\indent Encrypted:
\begin{verbatim}
   94 93 81 0E 62 47 30 86
\end{verbatim}

\subsection{Example 2}
\textit{World}
\\\indent Original:
\begin{verbatim}
   57 6F 72 6C 64 0A
\end{verbatim}
\indent Encrypted:
\begin{verbatim}
   24 0B A5 B2 CB C1 F2 8B 
\end{verbatim}

\subsection{Example 3}
\textit{Hello World}
\\\indent Original:
\begin{verbatim}
   48 65 6C 6C 6F 20 57 6F
   72 6C 64 0A
\end{verbatim}
\indent Encripted:
\begin{verbatim}
   E6 74 22 8A AC 1E 85 ED 
   B7 3C 26 3C 4B B4 F1 77
\end{verbatim}

\subsection{Example 4}
\textit{The quick brown fox jumps over the lazy dog}
\\\indent Original:
\begin{verbatim}
   54 68 65 20 71 75 69 63 
   6B 20 62 72 6F 77 6E 20 
   66 6F 78 20 6A 75 6D 70 
   73 20 6F 76 65 72 20 74 
   68 65 20 6C 61 7A 79 20 
   64 6F 67 0A
\end{verbatim}
\indent Encrypted:
\begin{verbatim}
   09 D1 3F 78 9D C7 66 B7 
   46 52 A9 9F 57 92 38 65 
   8B 40 39 1C 21 9E 77 D7 
   9B 84 62 AF E9 22 25 1D 
   96 61 A7 22 09 97 2C D2 
   16 F5 D8 38 E4 FF C6 86
\end{verbatim}

\section{Software Design}
We chose to implement DES completely in $C++$ for this project.
Both of the members our group were knowledgeable and comfortable
with $C++$ and in general the $C$ world. We felt we would have a more
generally usable and useful implementation if we went with $C++$ over
another language (Java, Python, ... ). We attempted to take advantage ac{OOP} but
were careful not to over do it and dive into downword spiral subclass's and
analysing of class cohesion. The $DES$ implementation is simply a class, with actions of encrypting and
decrypting. All state information is organized within the class. We then
implemented a $BlockMode$ class which implements a cipher block, which is
as you know, just a wrapper around $DES$. The user is then provided with
two small utility functions $encrypt$ \and $decrypt$.

@@

During the duration of the project we attempted to work in a {TDD} model.
All major functions and actions have associated unit-tests which we derived from various peices of
literature on DES. These unit test's were then hooked up to run using the Google Test Framework\cite{gtest}.

\section{Original Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 123456789ABCDEF and key 133457799BBCDFF1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04.
\\Test 1:
\\ \indent 10.856 seconds
\\Test 2:
\\ \indent 10.885 seconds
\\Test 3:
\\ \indent 10.912 seconds
\\\\Average:
\\ \indent 10.884 seconds
\section{Original Runtime Analysis}
\section{Revised Software design}
\section{Revised Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 123456789ABCDEF and key 133457799BBCDFF1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04.
\\Test 1:
\\ \indent 5.294 seconds
\\Test 2:
\\ \indent 5.321 seconds
\\Test 3:
\\ \indent 5.385 seconds
\\\\Average:
\\ \indent 5.333 seconds
\section{Revised Runtime Analysis}
\section{Developers manual}
\section{Users Manual}
